A linear inside-outside algorithm for detecting next generation sequencing errors in structured RNAs

### 2012-10-07 Recomb/results_RECOMB.tex
time
intro

\subsection{Time}
The applications for this algorithms implies a need for efficiency
and scalability. In Table~\ref{tab:time} we
present different times needed to compute the probabilities for
 every nucleotide at every positions for a vast set of parameters.

\begin{table}
\begin{center}
\begin{tabular}{llccc}
$|s|$&$|\Omega|$&\multicolumn{3}{c}{Number of mutations}\\\cline{3-5}
		 & 				  & 6   &  12  & 24\\\cline{3-5}
100  & 44				& 35s  & 238s & 1023s\\
300  & 44				& 135s & 594s &2460s\\

\end{tabular}
\end{center}
\caption{Time to compute all probabilities. The first column indicates the length, the second
 the size of $\Omega$ and  the column indexes indicate the number
 of mutations. $\alpha$ is
set at $0.5$, and $\beta=1.5$ and All sequences are generated randomly.}
\label{tab:time}
\end{table}

>>>>

\subsection{Time}
The applications for this algorithms implies a need for efficiency
and scalability. In Table~\ref{tab:time} we
present different times needed to compute the probabilities for
 every nucleotide at every positions for a vast set of parameters. For those test
 all the sequences were generated randomly, as the target secondary structure.

\begin{table}
\begin{center}
\begin{tabular}{lccc}
$|s|$&\multicolumn{3}{c}{Number of mutations}\\\cline{2-4}
		 			  & 6   &  12  & 24\\\cline{2-4}
100  				& 35s  & 238s & 1023s\\
300  			& 135s & 594s &2460s\\\cline{2-4}
		 						& 25   & 30   &			\\\cline{2-4}
300       &      &  3950s&     \\
500         & 5400s&       &      \\
\end{tabular}
\end{center}
\caption{Time to compute all probabilities. The first column indicates the length and  the column indexes indicate the number
 of mutations. $\alpha$ is
set at $0.5$, and $\beta=1.5$ and $|\Omega|=44$.}
\label{tab:time}
\end{table}
